---
title: "R Notebook"
output: html_notebook
---

Copy and paste the URL to the page on le.utah.gov that has the bills for the current legislative session. When you run the chunk, it will open a webdev window to the page with all the bills for the session. Click on each of the small + icons to open the "containers" on the page. This step is important because the rest of the code relies on those containers being opened. Keep that window open. 
```{r}
library(rvest, Chromote, openxlsx)

Bills <- read_html_live("https://le.utah.gov/DynaBill/BillList?session=2024GS")
Bills$view()
```

```{r}
#
column1 <- Bills %>% html_elements(" dt") %>%
  html_text()
#
column2.1 <- "https://le.utah.gov/"
#
column2.2 <- Bills %>% html_elements(".nlink") %>%
  html_attr("href")
#
column2 <- paste0(column2.1,column2.2)
#
column3 <- Bills %>% html_elements("em") %>% 
    html_text()
# Create a data frame
df <- data.frame(Column1 = column1, Column2 = column2, Column3 = column3)
# Print the data frame
print(df)
```

```{r}
openxlsx::write.xlsx(df,"Bills.xlsx")
```

#script to click selectors
#H.B. 1-49
Bills$click("#g1 > ul > li:nth-child(1) > a")
#H.B. 50-99
Bills$click("#g1 > ul > li:nth-child(2) > a")
#H.B. 100-149
Bills$click("#g1 > ul > li:nth-child(3) > a")
#H.B. 150-199
Bills$click("#g1 > ul > li:nth-child(4) > a")
#H.B. 200-249
Bills$click("#g1 > ul > li:nth-child(5) > a")
#H.B. 250-299
Bills$click("#g1 > ul > li:nth-child(6) > a")
#H.B. 300-349
Bills$click("#g1 > ul > li:nth-child(7) > a")
#H.B. 350-399
Bills$click("#g1 > ul > li:nth-child(8) > a")
#H.B. 400-449
Bills$click("#g1 > ul > li:nth-child(9) > a")
#H.B. 450-499
Bills$click("#g1 > ul > li:nth-child(10) > a")
#H.B. 500-549
Bills$click("#g1 > ul > li:nth-child(11) > a")
#H.B. 550-599
Bills$click("#g1 > ul > li:nth-child(12) > a")
#H.C.R. 1-49 
Bills$click("#g2 > ul > li > a")
#H.J.R. 1-49
Bills$click("#g3 > ul > li > a")
#H.R. 1-49
Bills$click("#g4 > ul > li > a")
#S.B. 1-49
Bills$click("#g5 > ul > li:nth-child(1) > a")
#S.B. 50-99
Bills$click("#g5 > ul > li:nth-child(2) > a")
#S.B. 100-149
Bills$click("#g5 > ul > li:nth-child(3) > a")
#S.B. 150-199
Bills$click("#g5 > ul > li:nth-child(4) > a")
#S.B. 200-249
Bills$click("#g5 > ul > li:nth-child(5) > a")
#S.B. 250-299
Bills$click("#g5 > ul > li:nth-child(6) > a")
#S.C.R. 1-49
Bills$click("#g6 > ul > li > a")
#S.J.R. 1-49
Bills$click("#g7 > ul > li > a")
#S.R. 1-49
Bills$click("#g8 > ul > li > a")
```
